Testing Quasar Unification: I. Radiative Transfer in Clumpy Winds

### 2015-12-18 paper.tex
few edits

Despite a number of successes, 
there are a some properties of the synthetic spectra
that are at odds with the observations. First, we find that the ratios of the 
EW of the \la\ and \mgline\ lines
to the EW of \civline\ is much lower than in the composite spectra. 
This problem has also been seen in simpler photoionization models for the 
BLR \citep{netzer1990}.
It may be that a larger region of very dense ($n_e\sim10^{10}$cm$^{-3}$) 
material is needed, which could correspond to a disc atmosphere or 
`transition region' (see e.g. Murray et al. 1995; Knigge et al. 1997).
\nocite{knigge1998} 
While modest changes to geometry may permit this, the initial grid search 
did not find a parameter space in which the \la\ or \mg\ EWs
were significantly higher (see section~\ref{sec:param_sens}. 
Second, we find that EWs increase
with inclination, to the extent that significantly denser
models can match the line EWs fairly well at low inclinations but will then
possess overly strong red wings to the BAL P-Cygni profiles at high inclinations
(see figures~\ref{fig:uvspec} and \ref{fig:sed}; also figure~\ref{fig:lobal}).
This angular dependence is expected from a model in which the BLR radiates
more isotropically than the disc, which in this case is foreshortened and limb darkened.
It appears to contradict observations, which show remarkably uniform emission
line properties in quasars and BALQSOs \citep{weymann1991,dipompeo2012b}. 
The angular distribution of the disc 
continuum and line emission
is clearly crucially important in determining the emergent broad 
line EWs, as suggested by, e.g., the analysis of \cite{risaliti2011}. 
We shall explore this question further in a future study.

>>>>

Despite a number of successes, 
there are a some properties of the synthetic spectra
that are at odds with the observations. First, we find that the ratios of the 
EW of the \la\ and \mgline\ lines
to the EW of \civline\ is much lower than in the composite spectra. 
This problem has also been seen in simpler photoionization models for the 
BLR \citep{netzer1990}.
It may be that a larger region of very dense ($n_e\sim10^{10}$cm$^{-3}$) 
material is needed, which could correspond to a disc atmosphere or 
`transition region' (see e.g. Murray et al. 1995; Knigge et al. 1997).
\nocite{knigge1998} 
While modest changes to geometry may permit this, the initial grid search 
did not find a parameter space in which the \la\ or \mg\ EWs
were significantly higher (see section~\ref{sec:param_sens}). 
Second, we find that EWs increase
with inclination, to the extent that significantly denser
models can match the line EWs fairly well at low inclinations but will then
possess overly strong red wings to the BAL P-Cygni profiles at high inclinations
(see figures~\ref{fig:uvspec} and \ref{fig:sed}; also figure~\ref{fig:lobal}).
This angular dependence is expected from a model in which the BLR radiates
more isotropically than the disc, which in this case is foreshortened and limb darkened.
It appears to contradict observations, which show remarkably uniform emission
line properties in quasars and BALQSOs \citep{weymann1991,dipompeo2012b}. 
The angular distribution of the disc 
continuum and line emission
is clearly crucially important in determining the emergent broad 
line EWs, as suggested by, e.g., the analysis of \cite{risaliti2011}. 
We shall explore this question further in a future study.
